\Huge Conferences in the Era of Expensive Carbon

### 2019-10-15 main.tex
CP

Thus, our second proposal is that {\bf ACM should impose a surcharge on
  conferences based on their carbon footprint.}  The charge should be low to
start and increase steadily and predictably, year on year.
%
Conference organizers can then choose how best to balance their
budgets---whether 
by decreasing per-participant emissions, decreasing (physical)
participation, increasing registration fees, soliciting additional corporate
sponsorship, or other means.  \iflater\mwh{Problem: We showed just above
  that it's hard to figure out what to do. Come back to this point here and
  say that the surcharge will spur bold choices?  Maybe say that these
  choices won't necessarily be bad, but could be really great?}\fi

@@

\bcp{See comments at this point about companies (MS, Google?) that are
  already doing this.}
% You probably know about Microsoft using an internal price for carbon  - it's mentioned here:
% https://unfccc.int/climate-action/momentum-for-change/financing-for-climate-friendly/microsoft-global-carbon-fee
% And this report is also instructive:
% https://download.microsoft.com/download/0/A/B/0AB2FDD7-BDD9-4E23-AF6B-9417A8691CF5/Microsoft%20Carbon%20Fee%20Impact.pdf

@@

A key issue in implementation of this proposal will be how to set a price
that reflects the true social cost of carbon, without unduly harming the
community.
%
Initial data gathering will play a role, and a steady and predictable annual
ramp on the price is a necessary component, but setting both the initial
price and the slope of the ramp will likely be difficult political
decisions.
%
One measurable target, in line with the latest evidence from climate
science, would be to halve emissions every decade from now on, following the
``Carbon Law'' proposed in a recent paper~\cite{Rockstrom}.  \bcp{Read the
  paper and cite it!}
% https://doi.org/10.1126/science.aah3443

>>>>

Thus, our second proposal is that {\bf ACM should impose a surcharge on
  conferences based on their carbon footprint.}  The charge should start low 
and increase steadily and predictably, year on year.
%
Conference organizers can then choose how best to balance their
budgets---whether 
by decreasing per-participant emissions, decreasing (physical)
participation, increasing registration fees, soliciting additional corporate
sponsorship, or other means.

@@

% \bcp{See comments at this point about companies (MS, Google?) that are
%   already doing this.}
% You probably know about Microsoft using an internal price for carbon  - it's mentioned here:
% https://unfccc.int/climate-action/momentum-for-change/financing-for-climate-friendly/microsoft-global-carbon-fee
% And this report is also instructive:
% https://download.microsoft.com/download/0/A/B/0AB2FDD7-BDD9-4E23-AF6B-9417A8691CF5/Microsoft%20Carbon%20Fee%20Impact.pdf

@@

A key issue in implementation of this proposal will be how to set a price
that reflects the true social cost of carbon, without unduly harming the
community.
%
Initial data gathering will play a role, and a steady and predictable annual
ramp on the price is a necessary component, but setting both the initial
price and the slope of the ramp will likely be difficult political
decisions.
%
One measurable target, in line with the latest evidence from climate
science, would be to halve emissions every decade from now on, following the
``Carbon Law'' proposed in a recent paper~\cite{Rockstrom1269}.  \bcp{Read the
  paper and cite it!
  https://doi.org/10.1126/science.aah3443
  }
